### 2023-06-26 manuscript.tex
avoid _ in bib [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/d3100d949030a0fa261397bd204b045bdfde8861.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/d3100d949030a0fa261397bd204b045bdfde8861/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5382597999

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/a4a64794fe7e965163e5f2ac58d0c097945ec124/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/a4a64794fe7e965163e5f2ac58d0c097945ec124}{stain/2022-fdo-paper@a4a6479}
on June 26, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/d3100d949030a0fa261397bd204b045bdfde8861/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/d3100d949030a0fa261397bd204b045bdfde8861}{stain/2022-fdo-paper@d3100d9}
on June 26, 2023.
